The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
acknowledgements
fig2 caption

(ref:lcres) Varying scale in landcover resolution. For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m. Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution. B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution. C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions. D) Mean graph strength of individuals was weaker during the summer compared to the winter months.

@@

<!-- add jack -->

We thank all members of the Wildlife Evolutionary Ecology Lab, including K.
Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for
their comments on previous versions of this manuscript as well as D. C. Schneider
for inspiration and helpful discussions about scale. Funding for this study was
provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery
Grant to EVW.

>>>>

(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale. For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m. Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution. B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution. C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions. D) Mean graph strength of individuals was weaker during the summer compared to the winter months.

@@

We thank all members of the Wildlife Evolutionary Ecology Lab, including J. Hendrix, K.
Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for
their comments on previous versions of this manuscript as well as D. C. Schneider
for inspiration and helpful discussions about scale. Funding for this study was
provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery
Grant to EVW.
